---
title: "Weight of Fish"
author: "Ashley Cook"
date: "July 19, 2021"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
  

### Best Two regressor model
  
Best two regression models are height and width. 

```{r}
Perchmodel <-lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```
  
The adjusted r-squared is 0.94 and the residual standard error is 85.17, with a p-value of 2.2e-16


## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
 L1, L3 are the best two regression models. Best regression model is everything.

### Best Models

```{r}
Pikebest <-lm(Weight~.,data=Pike)
summary.lm(Pikebest)
```
  
 The r-squared is 0.9794 and the residual error is 70.86. The p-value is 8.679. This is the best model.


### Best Two regressor model

```{r}
Piketwo <-lm(Weight~Length1+Length3, data=Pike)
summary.lm(Piketwo)
```
  
This model summarizes our best two regression models. The residual standard error is 92.56. The r-squared is 0.9649 and the p-value is 2.572e-11. The smallest p-value has the best results. 

## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```
  
Best regression model is all of them. The two best regression models is L1, L3.


### Best Models

```{r}
Roachrock <-lm(Weight~.,data=Roach)
summary.lm(Roachrock)
```
  
The residual standard error is 37.58. The r-squared is 0.821 and the p-value is 1.028e-05. This mdoel holds the smallest p-value out of all the models we did so far above.

### Best Two regressor model

```{r}
Roachbest <-lm(Weight~Length1+Length3, data=Roach)
summary.lm(Roachbest)
```
  
The residual standard error is 36.83. The r-squared is 0.8281 and the p-value is at 1.23e-07. This has the second to smallest p-value out of all the charts/models.
## Final Summary Statements